Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-03-29 cover-letter/mu1y11-tlp-mn-190329-response-reviwers.tex
response letter and minor cleanup

\documentclass{mu-soton-letter}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We are grateful to the reviewers for their careful evaluation of the manuscript
and for their constructive comments. We have responded to their specific concerns
as detailed below:

@@

\textcolor{black!50}
{\emph{The submitted manuscript reports on a dual-channel modular probe assembly for NMR spectroscopy and imaging on microliter samples.
  The reported probe is an ''improved'' version of the one reported by the same authors in JMR in 2016 (Ref. 25).
  These improvements are:
  1)Dual channel (1H/15N or 1H/13C) instead of single channel (1H).
  2)Simplified fabrication and assembly of the probe parts, with significantly improved "versatility".}}

@@

  \begin{reviewer}
  The work presented in this manuscript deserve to be published. However, since it is a purely "technical" work, I would like to see the "technical content" described in more details.
  I think that the authors idea to have the drawings and the CAD files of the probe stored in a "open access" website is certainly good. However, I would like to see many more details of the probe design directly in the manuscript text, drawings, schematics, and figure captions.
\end{reviewer}

@@

\textcolor{black!50}{ \textbf{Detailed comments:}}

\begin{reviewer}
1) PAGE 1:  I would definitely add more relevant literature on "microfluidic NMR probes" such as:
\end{reviewer}
-Swyer, Ian, et al. "Digital microfluidics and nuclear magnetic resonance spectroscopy for in situ diffusion measurements and reaction monitoring" Lab on a Chip 19, 641 (2019).

Added in removable device

@@

Added in flow probe

@@

Added in flow probe

All of the suggested references are added in the introduction. Only the first article by Swyer, Ian, et al. describes a functional and exchangeable microfluidic device, rest of the references are added in the microfluidic flow probes for NMR.

\begin{reviewer}
2) FIGURE 1: Add in the caption the thickness of each "layer" (PCBs, spacer, microfluid device). Specify also the thickness of the Cu layers on the PCBs (this might be relevant for the spectral resolution due to a different thickness of the "air layers" in close proximity to the sample). Some of these dimensions are reported in the text but it would be nice to have all dimensions also in this figure caption.
\end{reviewer}
All the details are added in the figure caption.

\begin{reviewer}
3) FIGURE 1: From the drawings it seems to me that the Al spacer is short-circuiting the transmission line. Please clarify this point.
\end{reviewer}
The spacer is made of PMMA, hence it is non-conducting. In the caption of figure 5 it is added that an insulating solder mask layer on the copper prevents accidental short-circuiting.
\begin{reviewer}
4) PAGE 2, LINE 32, RIGHT: Indicated which specific semi-rigid coaxial cables are used.
\end{reviewer}
RG 402, 50 Ohm added to the text.
\begin{reviewer}
5) PAGE 2, LINE 48, RIGHT: Indicated which specific capacitors are used.
\end{reviewer}
The values and the manufacturer part number of all the circuit elements are added in table 2.

\begin{reviewer}
6) PAGE 2, LINE 50, RIGHT: Indicated which specific connectors are used (in the probe base as well as in the probe PCB).
\end{reviewer}
All the details are added in the text.

\begin{reviewer}
7) PAGE 3, LINE 30, LEFT: For the case in which the microfluidic device is used as "passive sample holder", how the microfluidic device is sealed?
\end{reviewer}
By an optical adhesive film, added in the text.

\begin{reviewer}
8) PAGE 3, LINE 58, LEFT: It would be useful for the reader to add the approximate values for the magnetic susceptibility of as many as possible probe materials (in order of importance: PMMA, Cu, RO3035, FR4, Al).
\end{reviewer}
Susceptibilities are added in table 1.

\begin{reviewer}
9) PAGE 3, LINE 48, RIGHT: Typo "resnance".
\end{reviewer}
Resonance is corrected in the text.

@@

\begin{reviewer}
11) FIGURE 5: Add a detailed picture and/or drawing of the tuning\&matching PCB (the TMPCB in the authors notation), give the position on the PCB of all the components (capacitors, variable capacitors, and inductors), and give all values (and model and manufacturer, particularly for the inductors and the variable capacitors) of these components. Increase the font size (it is too small).
\end{reviewer}
The picture of TMPCB and detector PCB 3 and 5 are added. Details of all the circuit elements are added in the table 2.
\begin{reviewer}
12) PAGE 4, LINE 6, RIGHT: It is not clear to me the meaning of "0.5 mm magnet wire".
\end{reviewer}
copper wire of diameter 0.5 mm.
\begin{reviewer}
13) FIGURE 6: I would scale up the figure to full column width. The font size is a bit too small. In the caption there is a typo ("at and").
\end{reviewer}
The figure is scaled up with bigger fonts
\begin{reviewer}
14) FIGURE 7: Is it really true that the FR4 gives a worse spectral resolution with respect to R03035 because of "glass fibre rovings" as mentioned at PAGE 4, LINE 51, RIGHT ? Is the thickness of the Cu layer the same on both substrates ? Is the magnetic susceptibility of the two material similar ? The R03035 has significantly lower tensile modulus with respect to FR4. I wonder if this might help in having a better "mechanical fit" in the mounting, which might reduce the presence of "air voids".
\end{reviewer}
The resolution is directly related to the B0 field homogeneity. The field maps of the two materials under the same conditions show the fringes observed in the FR4 material. These fringes are caused by glass fiber rovings which can be seen optically. Magnetic susceptibility of the two materials is different, but the materials are more than 0.1 mm far from the sample and hence will have minimal effect on the B0 field. The mechanical fit is similar in both the designs as the chip is inserted without resistance in both the cases. The air voids are expected to be of the volume in both the designs as the spacer is same.
\begin{reviewer}
15) FIGURE 7: Add a drawing or picture of the "constriction" (with scale bar or, even better, indicated dimensions) where we can see the width of the constriction, the length of the constriction, and the width of the gap between the constriction and the "external" metal.
\end{reviewer}
The constriction drawing with dimensions is added in the figure 5.
\begin{reviewer}
16) PAGE 6, LINE 59, LEFT: Specify the material used as replacement of Al for the sleeve in the imaging experiments?
\end{reviewer}
Shorter aluminium tube with 3D printed part on top to match the probe height was used.

\textbf{Reviewer 2}

\textcolor{black!50}{
\emph{In this manuscript, the authors report the design and construction of a modular NMR probe dedicated to microfluidics applications.  The authors show 1D proton and HSQC spectra as well as images of mouse liver slices acquired with this probe. The proton RF coil design used has been published previously by the same group. This probe design is interesting for the microfluidics community especially since the authors make available all the drawings on github.}}

\textcolor{black!50}{ \textbf{Major comments:}}

\begin{reviewer}
1.      The authors claim that the RF homogeneity is "excellent", they must show B1 maps to support this claim.  On page 5, in the paragraph starting with "The RF field?" it should be 180/90 and not 810/90.
\end{reviewer}
The 1H nutation diagram is added as figure 8. It is indeed 810/90 as can be seen in figure 8.
\begin{reviewer}
2.      Are the B0 maps in Figure 7 acquired at 14T?  Please specify. Please show B0 and B1 maps both at 11.7 and 14.1T.
\end{reviewer}
B0 filed maps were acquired in 11.7 T. It is added in the text. B0 field maps can only be acquired at 11.7 T due to the availability of the gradient unit.
\begin{reviewer}
3.      The images of liver slices are not convincing.  If three different sequences are used the authors should adapt the parameters to obtain meaningful contrast. Please list all the acquisition parameters for the different sequences. In the caption of figure 11, should be "cut liver slices".
\end{reviewer}
It must be noted that the images were taken to demonstrate the proof of principle to obtain an MR image of a tissue slice using the current setup. The optimisation of the imaging parameters and the tissue culture are underway to obtain a physiologically relevant dataset. Parameters for different pulse sequences will be added in the methods section.
\begin{reviewer}
4.      The Results and Discussion section is a mixture or Results and Experimental parameters (in particular NMR/MRI acquisition parameters). Please move all the experimental parameters into the Methods section under a subsection dedicated to NMR/MRI acquisitions.
\end{reviewer}
All the experimental parameters have been moved to a subsection in the methods section.

\textcolor{black!50}{ \textbf{Minor comments:}}
\begin{reviewer}
1.      Please reformulate the last sentence on page 1 starting with "The probe is designed".
\end{reviewer}
??

>>>>

% !TEX program = pdflatex
\documentclass{mu-soton-letter}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We are grateful to the reviewers for their careful evaluation of the manuscript
and for their constructive comments. We have responded to their specific concerns
as follows:

@@

%\textcolor{black!50}
\begin{reviewer}
{The submitted manuscript reports on a dual-channel modular probe assembly for NMR spectroscopy and imaging on microliter samples.
  The reported probe is an ''improved'' version of the one reported by the same authors in JMR in 2016 (Ref. 25).
  These improvements are:
  1)Dual channel (1H/15N or 1H/13C) instead of single channel (1H).
  2)Simplified fabrication and assembly of the probe parts, with significantly improved "versatility".}

@@

  The work presented in this manuscript deserve to be published. However, since it is a purely "technical" work, I would like to see the "technical content" described in more details.
  I think that the authors idea to have the drawings and the CAD files of the probe stored in a "open access" website is certainly good. However, I would like to see many more details of the probe design directly in the manuscript text, drawings, schematics, and figure captions.
\end{reviewer}

@@

\begin{reviewer}
\textbf{Detailed comments:}
1) PAGE 1:  I would definitely add more relevant literature on "microfluidic NMR probes" such as:
-Swyer, Ian, et al. "Digital microfluidics and nuclear magnetic resonance spectroscopy for in situ diffusion measurements and reaction monitoring" Lab on a Chip 19, 641 (2019).

%Added in removable device

@@

%Added in flow probe

@@

%Added in flow probe
\end{reviewer}
All of the suggested references have been added to the introduction.

\begin{reviewer}
2) FIGURE 1: Add in the caption the thickness of each "layer" (PCBs, spacer, microfluid device). Specify also the thickness of the Cu layers on the PCBs (this might be relevant for the spectral resolution due to a different thickness of the "air layers" in close proximity to the sample). Some of these dimensions are reported in the text but it would be nice to have all dimensions also in this figure caption.
\end{reviewer}
All the details have been added to the figure caption.

\begin{reviewer}
3) FIGURE 1: From the drawings it seems to me that the Al spacer is short-circuiting the transmission line. Please clarify this point.
\end{reviewer}
The spacer is made of PMMA, hence it is non-conducting. This is pointed out
clearly in the revised manuscript. Also, the caption of figure 5 now points out
that an insulating solder mask layer on the copper prevents accidental short-circuiting.
\begin{reviewer}
4) PAGE 2, LINE 32, RIGHT: Indicated which specific semi-rigid coaxial cables are used.
\end{reviewer}
RG 402, 50 Ohm added to the text.
\begin{reviewer}
5) PAGE 2, LINE 48, RIGHT: Indicated which specific capacitors are used.
\end{reviewer}
The values and the manufacturer part number of all the circuit elements
have been added in table 2.

\begin{reviewer}
6) PAGE 2, LINE 50, RIGHT: Indicated which specific connectors are used (in the probe base as well as in the probe PCB).
\end{reviewer}
The detailed specficications of the connectors are now provided in the text.

\begin{reviewer}
7) PAGE 3, LINE 30, LEFT: For the case in which the microfluidic device is used as "passive sample holder", how the microfluidic device is sealed?
\end{reviewer}
Using an optical adhesive film, as added to the revised manuscript.

\begin{reviewer}
8) PAGE 3, LINE 58, LEFT: It would be useful for the reader to add the approximate values for the magnetic susceptibility of as many as possible probe materials (in order of importance: PMMA, Cu, RO3035, FR4, Al).
\end{reviewer}
All relevant known susceptibilities are now listed in Table 1.

\begin{reviewer}
9) PAGE 3, LINE 48, RIGHT: Typo "resnance".
\end{reviewer}
corrected.

@@

\begin{reviewer}
11) FIGURE 5: Add a detailed picture and/or drawing of the tuning\&matching PCB (the TMPCB in the authors notation), give the position on the PCB of all the components (capacitors, variable capacitors, and inductors), and give all values (and model and manufacturer, particularly for the inductors and the variable capacitors) of these components. Increase the font size (it is too small).
\end{reviewer}
Full information on the TMPCB as well as the other two PCB components is now
included in Figure 5. The relationship between the circuit diagram and the PCB
layouts is now also indicated clearly, andd etails of all the circuit
elements are given in Table 2.
\begin{reviewer}
12) PAGE 4, LINE 6, RIGHT: It is not clear to me the meaning of "0.5 mm magnet wire".
\end{reviewer}
copper wire of diameter 0.5 mm; the text has been corrected accordingly.
\begin{reviewer}
13) FIGURE 6: I would scale up the figure to full column width. The font size is a bit too small. In the caption there is a typo ("at and").
\end{reviewer}
The figure has been scaled up, uses bigger fonts, and the typo has been corrected.
\begin{reviewer}
14) FIGURE 7: Is it really true that the FR4 gives a worse spectral resolution with respect to R03035 because of "glass fibre rovings" as mentioned at PAGE 4, LINE 51, RIGHT ? Is the thickness of the Cu layer the same on both substrates ? Is the magnetic susceptibility of the two material similar ? The R03035 has significantly lower tensile modulus with respect to FR4. I wonder if this might help in having a better "mechanical fit" in the mounting, which might reduce the presence of "air voids".
\end{reviewer}
The resolution is directly related to the B0 field homogeneity.
The field maps of the two materials under the same conditions show the fringes
observed in the FR4 material. These fringes are caused by glass fiber
rovings which can be seen optically.
The mechanical fit is similar in both the designs as the chip is inserted
without resistance in both the cases. The vertical boundaries between the chip and the
detector planes do not contribute to susceptibility broadening, as they are parallel
to the magnetic field; therefore the air voids between the chip and the detector
are not relevant. The Cu layers in both materials are about 35 $\mu$m thick,
and their horizontal edges (which define the constriction geometry) are unlikely
to be a dominant factor in the observed line widths.
\begin{reviewer}
15) FIGURE 7: Add a drawing or picture of the "constriction" (with scale bar or, even better, indicated dimensions) where we can see the width of the constriction, the length of the constriction, and the width of the gap between the constriction and the "external" metal.
\end{reviewer}
The constriction drawing with dimensions is added in the figure 5.
\begin{reviewer}
16) PAGE 6, LINE 59, LEFT: Specify the material used as replacement of Al for the sleeve in the imaging experiments?
\end{reviewer}
A shorter aluminium housing was used, combined with a 3D printed (ABS plastic)
housing for the detection part of the probe. This is pointed out clearly in the
revised manuscript.

\clearpage
\textbf{Reviewer 2}

\begin{reviewer}
  {In this manuscript, the authors report the design and construction of a modular NMR probe dedicated to microfluidics applications.  The authors show 1D proton and HSQC spectra as well as images of mouse liver slices acquired with this probe. The proton RF coil design used has been published previously by the same group. This probe design is interesting for the microfluidics community especially since the authors make available all the drawings on github.}

  \textbf{Major comments:}

1.      The authors claim that the RF homogeneity is "excellent", they must show B1 maps to support this claim.  On page 5, in the paragraph starting with "The RF field?" it should be 180/90 and not 810/90.
\end{reviewer}
In order to document the RF homogeneity, we have added the 1H nutation diagram
as Figure 8. The quantity referred to by the reviewer is indeed the ratio of the
amplitudes of signals following a 810$^\circ$ pulse and a 90$^\circ$ pulse, respectively.
This quanitity is commonly used to quantify RF homogeneity in commercial probes,
and is often referred to as "810/90 ratio". It is now explained clearly in Figure 8.
\begin{reviewer}
2.      Are the B0 maps in Figure 7 acquired at 14T?  Please specify. Please show B0 and B1 maps both at 11.7 and 14.1T.
\end{reviewer}
B0 filed maps were acquired in 11.7 T, as now indicated in the text. B0 field maps could
 only be acquired at 11.7 T, since we do not have a gradient unit available on
 our 14.1T magnets.

\begin{reviewer}
3.      The images of liver slices are not convincing.  If three different sequences are used the authors should adapt the parameters to obtain meaningful contrast. Please list all the acquisition parameters for the different sequences. In the caption of figure 11, should be "cut liver slices".
\end{reviewer}
As requested, detailed parameters for the different pulse
sequences have been added to the methods section.
We agree with the reviewer that the contrast in the images shown could be
improved. However,
the images are merely providing a proof
of principle that the probe is capable to support MR microimaging, and no
conclusions going beyond this are drawn from this data in the manuscript.
Optimisation of the parameters for a particular sample class was outside of the
scope of the work presented here. That said, the images do exhibit some
structural contrast, and features in the slices can be correlated with the
optical micrograph. The optimisation of the imaging parameters and the
tissue culture are currently underway, but will be reported separately.

\clearpage
\begin{reviewer}
4.      The Results and Discussion section is a mixture or Results and Experimental parameters (in particular NMR/MRI acquisition parameters). Please move all the experimental parameters into the Methods section under a subsection dedicated to NMR/MRI acquisitions.
\end{reviewer}
All the experimental parameters have been moved to a subsection in the methods section.

\textcolor{black!50}{ \textbf{Minor comments:}}
\begin{reviewer}
1.      Please reformulate the last sentence on page 1 starting with "The probe is designed".
\end{reviewer}
As suggested, we have reformulated the sentence, and connected it with the following one:
"The probe is optimised for proton detected double resonance, with the
second channel tunable to different nuclei\ldots"
\vspace{3cm}

Again, we are grateful to the reviewers for their constructive criticism, and
we are confident that the above changes adequately address their concerns.

### 2019-03-29 ms5n17-tlp-mn-180216-001.tex
started response letter
formated the coverletter and citations
response letter and minor cleanup

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
%\linenumbers
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

been described~\cite{Spengler-2014,Spengler-2016,gream_2016,swyer2019digital}. \cbend

In this paper we present a novel modular probe designed for generic
microfluidic-NMR experiments. The design is based on a transmission line
detector~\cite{stripline_jan,gream_2016} using inexpensive
printed circuit board (PCB) technology. A modular design ensures that detectors of
different geometry and size can be easily exchanged.
The NMR detector (including the tuning and matching circuit) is connected to the probe
skeleton through detachable connectors. Modularity of the probe not only allows
fast optimisation of the detector but also facilitates the use of dedicated detectors
for different microfluidic devices on a single probe base.
Once the probe base is in place, additional detectors can be manufactured
within 2-3 days for less than $\sim$200 $\geneuro$.
The probe is designed for proton detected double resonance.
The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
such as aluminium profiles of standard size, with only a small number of
custom-machined parts holding the structure together.
Detailed construction drawings and a complete set of CAD files is
available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
The planar geometry of the detector accommodates exchangeable microfluidic devices
which can be designed freely for specific experimental requirements as long as the
overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative positioning.

@@

The base, the scaffold assembly and the tuning and matching PCB all have a free circular
axial bore providing access from the bottom of the probe, which can be used for
temperature and environmental control and/or fluidic connections to the sample as
needed. The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them. \cbstart The spacer is made from a 1 mm thick PMMA sheet.\cbend  The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper
planes, each with a constriction at the centre.  This geometry gives rise to an
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field
and the detection sensitivity
onto the sample area.
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2)
and the scaffold assembly with screws.
An exchangeable microfluidic device (1) can be inserted from the top of the detector.
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film when using the device as passive sample holder.\cbend
 The microfluidic device is held in place by the spacer
between the two PCB planes coinciding the sample chamber with the constriction on the
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment.
Since the detector assembly is attached to the probe base through SMP
connectors, it can easily be exchanged.
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

@@

\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png}
\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and
$^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from
2.5$\mu$l sample volume at 14.1 T. Glucose HSQC spectrum was acquired in 12
minutes from a 100 mM sample. Ubiquitin HSQC spectrum was acquired in 400
minutes from a 1 mM sample.} \label{fig:HSQC} \end{figure}
%$
\cbdelete
The probe can also be used to acquire micro magnetic resonance (MR) images using
a Bruker micro-gradient unit. To this effect, the aluminium probe sleeve must be
replaced by an electrically insulating material in order to avoid image
distortions due to eddy currents in the sleeve.\cbstart In the current experiments a shorter aluminium tube with 3D printed top part to match the probe height was used.\cbend  \fig{fig:tisli} shows MR images
of mouse liver tissue slice immersed in DMEM cell growth medium. The slice was
placed in a microfluidic device with circular sample chamber centred at the
detector location, as shown in \fig{fig:tisli}(A). The image shown in
\fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with; the lateral dimensions of all MR images in \fig{fig:tisli} are 512$\times$512 pixels at a resolution of 30~$\mu$m. \fig{fig:tisli}(C) shows a
RARE image using the same parameters. A spin echo image is shown in
\fig{fig:tisli}(D). Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images.

>>>>

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
%\linenumbers
\biboptions{sort&compress}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

been described~\cite{Spengler-2014,Spengler-2016,gream_2016,swyer2019digital}.\cbend

In this paper we present a novel modular probe designed for generic
microfluidic-NMR experiments. The design is based on a transmission line
detector~\cite{stripline_jan,gream_2016} using inexpensive
printed circuit board (PCB) technology. A modular design ensures that detectors of
different geometry and size can be easily exchanged.
The NMR detector (including the tuning and matching circuit) is connected to the probe
skeleton through detachable connectors. Modularity of the probe not only allows
fast optimisation of the detector but also facilitates the use of dedicated detectors
for different microfluidic devices on a single probe base.
Once the probe base is in place, additional detectors can be manufactured
within 2-3 days for less than $\sim$200 $\geneuro$.
The probe is optimised for proton detected double resonance, with the
second channel tunable to different nuclei such as $^{13}$C, $^{15}$N, or
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
such as aluminium profiles of standard size, with only a small number of
custom-machined parts holding the structure together.
Detailed construction drawings and a complete set of CAD files is
available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
The planar geometry of the detector accommodates exchangeable microfluidic devices
which can be designed freely for specific experimental requirements as long as the
overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative positioning.

@@

The base, the scaffold assembly and the tuning and matching PCB all have a free circular
axial bore providing access from the bottom of the probe, which can be used for
temperature and environmental control and/or fluidic connections to the sample as
needed. The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them. \cbstart The spacer is made from a 1 mm thick PMMA sheet.\cbend  The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper
planes, each with a constriction at the centre.  This geometry gives rise to an
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field
and the detection sensitivity
onto the sample area.
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2)
and the scaffold assembly with screws.
An exchangeable microfluidic device (1) can be inserted from the top of the detector.
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film (MicroAmp, AB Applied Biosystems)
when using the device as passive sample holder.\cbend
 The microfluidic device is held in place by the spacer
between the two PCB planes coinciding the sample chamber with the constriction on the
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment.
Since the detector assembly is attached to the probe base through SMP
connectors, it can easily be exchanged.
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

@@

\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png}
\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and
$^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from
2.5$\mu$l sample volume at 14.1 T. Glucose HSQC spectrum was acquired in 12
minutes from a 100 mM sample. Ubiquitin HSQC spectrum was acquired in 400
minutes from a 1 mM sample.} \label{fig:HSQC} \end{figure}
%$
\cbdelete
The probe can also be used to acquire micro magnetic resonance (MR) images using
a Bruker micro-gradient unit. To this effect, the aluminium probe sleeve must be
replaced by an electrically insulating material in order to avoid image
distortions due to eddy currents in the sleeve.\cbstart\
A shorter aluminium tube with 3D printed top part (made from ABS plastic)
to match the probe height was used.\cbend  \fig{fig:tisli} shows MR images
of mouse liver tissue slice immersed in DMEM cell growth medium. The slice was
placed in a microfluidic device with circular sample chamber centred at the
detector location, as shown in \fig{fig:tisli}(A). The image shown in
\fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with; the lateral dimensions of all MR images in \fig{fig:tisli} are 512$\times$512 pixels at a resolution of 30~$\mu$m. \fig{fig:tisli}(C) shows a
RARE image using the same parameters. A spin echo image is shown in
\fig{fig:tisli}(D). Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images.
